Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-01 yfcc100m/paper/vldb2020/eval.tex
Minor changes and reformating

The Yahoo! Flickr Creative Commons 100m (YFCC100M) dataset is a
large collection of 100 million public Flickr media objects.
It contains approximately 99.2 million images and 0.8 million videos
with metadata characterized by 25 fields such as the identifier,
the user, the date the media was taken/uploaded,
the location in longitude/latitude coordinates,
and the device the media was captured.
The metadata also provides information including the URL to
download the media object, a title, a description, user and
auto-generated tags, and Creative Commons license information.
The YFCC100M dataset also used a deep learning approach to generate
autotags data which is a set of comma-separated concepts such as people,
scenery, objects, and animals and confidence scores
generated from 1,570 trained Caffe classifiers ~\cite{Thomee_2016}.

@@

For all our experiments, we use 2 servers, one hosting VDMS server and
another hosting MySQL server. Both servers have a dual-socket INTEL XEON XXXXX,
each cpu with 28 physical cores with multithreading enabeled,
for a total of 112 logical cores per server.
The server hosting MySQL has 256GB of DDR4 DRAM, while the server hosting VDMS
has 64GB of DDR4 DRAM. Both servers run Ubuntu 16.04.
We use MySQL version XXXXX.

Figure \ref{figure:systems} shows a logical view of the difference between the
interaction of the client application (which wants to retrieve metadata and
imaged) with VDMS (left) and MySQL + Apache HTTP Server (right).
It is worth noting that the images are stored in a shared repository
(ext4 filesystem on a RAID 6 configuration of 16TB) that both Apache WebServer
and VDMS have direct access. In the case of MySQL, metadata is stored in an
attached SSD disk. Even if VDMS has native support for Optane Persistent Memory,
we do not use it in this experiment because of fairness of comparison w.r.t
MySQL. The benefits of Persistent Memory on metadata operations is left
for another paper, and outside the scope of this evaluation.
For this experiment then, we simply use a similar attached SSD disk to store
metadata (even if VDMS Graph store is designed for PM, it can deliver good
performance when using SSDs directly).

@@

As a baseline, we implemented a similar database system, depicted in Figure~\ref{fig:systems}, comprised of a combination of widely available and out-of-the-box components: MySQL Server 5.7, Apache Web Server, and OpenCV.  Each database system used the following configuration: Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered} Platinum 8180 CPU @ 2.50GHz (Skylake) server running Ubuntu 16.04.

>>>>

The Yahoo! Flickr Creative Commons 100m (YFCC100M) dataset is a
large collection of 100 million public Flickr media objects.
It contains approximately 99.2 million images and 0.8 million videos
with metadata characterized by 25 fields such as the identifier,
the user, the date the media was taken/uploaded,
the location in longitude/latitude coordinates,
and the device the media was captured.
The metadata also provides information including the URL to
download the media object, a title, a description, user and
auto-generated tags, and Creative Commons license information.
The YFCC100M dataset also used a deep learning approach to generate
autotags data which is a set of comma-separated concepts such as people,
scenery, objects, and animals and confidence scores
generated from 1,570 trained Caffe classifiers \cite{Thomee_2016}.
We have also used feature vectors generated for every image and first frame
of every video \cite{features} to implement similarity search.

@@

For all our experiments, we use 2 servers, one hosting VDMS server and
another hosting MySQL server. Both servers have a dual-socket
Intel\textsuperscript{\textregistered}
Xeon\textsuperscript{\textregistered} Platinum 8180 CPU @ 2.50GHz (Skylake),
each CPU with 28 physical cores with multithreading enabeled,
for a total of 112 logical cores per server.
The server hosting MySQL has 256GB of DDR4 DRAM, while the server hosting VDMS
has 64GB of DDR4 DRAM. Both servers run Ubuntu 16.04.
We use MySQL version XXXXX.

As a baseline, we implemented a similar database system comprised of a
combination of widely available and out-of-the-box components: MySQL Server 5.7,
Apache Web Server, and OpenCV.
Figure \ref{figure:systems} shows a logical view of the difference between the
interaction of the client application (which wants to retrieve metadata and
imaged) with VDMS (left) and the baseline (right).
It is worth noting that the images are stored in a shared repository
(ext4 filesystem on a RAID 6 configuration of 16TB) that both Apache WebServer
and VDMS have direct access. In the case of MySQL, metadata is stored in an
attached SSD disk. Even if VDMS has native support for Optane Persistent Memory,
we do not use it in this experiment because of fairness of comparison w.r.t
MySQL. The benefits of Persistent Memory on metadata operations is left
for another paper, and outside the scope of this evaluation.
For this experiment then, we simply use a similar attached SSD disk to store
metadata (even if VDMS Graph store is designed for PM, it can deliver good
performance when using SSDs directly).

@@

### 2020-02-01 yfcc100m/paper/vldb2020/vdms-vldb2020.tex
Minor changes and reformating

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

@@

@@

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references).

>>>>

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

@@

\section{Acknowledgments}

We have to acknowledge Philip, Vishakha, Nilesh, and any other reviewer.

@@

% \subsection{References}
% Generated by bibtex from your ~.bib file.  Run latex,
% then bibtex, then latex twice (to resolve references).
